A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-08 tex/sec5-synthesis.tex
[ tex ] Revise the statement of Trichotomy again

\begin{corollary}[Trichotomy on Raw Terms]\label{cor:trichotomy}
  Exactly one of the following holds:
  \begin{enumerate}
    \item $\isTerm{t}$ is synthesising and\/ $\Gamma |-_{\Sigma, \Omega} \isTerm{t} : A$ for some type $A$.
    \item $\isTerm{t}$ is synthesising but\/ $\Gamma \not|-_{\Sigma, \Omega} \isTerm{t} : A$ for any type $A$.
    \item $\isTerm{t}$ is not synthesising.
  \end{enumerate}
\end{corollary}
\begin{proof}
  Combine  \Cref{lem:soundness-completeness,thm:mode-preprocessing} with \Cref{thm:bidirectional-type-synthesis}.

>>>>

\begin{corollary}[Trichotomy on Raw Terms]\label{cor:trichotomy}
  For any mode-correct bidirectional type system $(\Sigma, \Omega)$, 
  exactly one of the following holds:
  \begin{enumerate}
    \item $\erase{\Gamma} |-_{\Sigma, \Omega} \isTerm{t}^{\syn}$ and\/ $\Gamma |-_{\Sigma, \Omega} \isTerm{t} : A$ for some type $A$.
    \item $\erase{\Gamma} |-_{\Sigma, \Omega} \isTerm{t}^{\syn}$ but\/ $\Gamma \not|-_{\Sigma, \Omega} \isTerm{t} : A$.
    \item $\erase{\Gamma} \not|-_{\Sigma, \Omega} \isTerm{t}^{\syn}$.
  \end{enumerate}
\end{corollary}
\begin{proof}
  Combine  \Cref{lem:soundness-completeness,thm:mode-preprocessing} with \Cref{thm:bidirectional-type-synthesis}.
